---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# historicalBorders

<!-- badges: start -->
<!-- badges: end -->

This package allows users to visualize political boundaries for a selected continent, region, or country at a specific point in history. Building upon existing ways of visualizing spatial data, we aimed to create a way for R users to map data over historic borders from the last 200 years. In this, we can visualize data in a way that makes sense historically — showing the borders that people throughout history would have understood and lived within. Maps generated with this package are derived from the [historic-basemaps](https://github.com/aourednik/historical-basemaps) repository.

## Installation

You can install the development version of historicalBorders from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("lucinaob/historicalBorders")
```

## Example

To create a historic map using this package, you only have to specify a part of the world and a year! For example, to map the world in 1800, we only have to call:

```{r example, message=FALSE, warning=FALSE}
library(historicalBorders)
mapWorld(1800)
```

The package also allows users to map data onto historic maps utilizing the `ggplot2` package. For example, the map below visualized population data of the world at 1900 onto a historic map (greyed out regions indicate no data)

```{r, echo=FALSE}
options(scipen = 999)
```


```{r cars}
mapWorld(1900, dataset = population1900, aesthetics = aes(fill = POP/1000000)) + 
  labs(fill = "Population (Millions)")
```

