---
title: "overview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(historicalBorders)
```

`historicalBorders` is an R package for producing visualizations of historical maps. Utilizing the `sf` and `ggplot2` packages, `historicalBorders` allows users to plot data over historical borders, from the 1800s until today. Maps are available in 50-year increments, built off of the [\`historic-basemaps\`](https://github.com/aourednik/historical-basemaps) repo.

## Base Maps

To plot the whole world at a given point in time, a user can use the `mapworld` function, specifying a certain year:

```{r}
mapworld(1800)
```

If a user gives a year that is not included in the dataset, the function will display the map from the closest year:

```{r}
mapworld(1875)
```

## Visualizing Region Options 

The `optionsRegions()` function allows users to see a data frame display of regions within a specified continent by inputting`optionsRegions(["continent"])`:

```{r}
options_regions("Africa")
```

## Visualizing Year Options 

To visualize the years available to choose from, users can call the `optionsYears()` function: 

```{r}
optionsYears()
```

## Mapping Continents

If a user only wants to visualize a certain continent, they can do so by choosing a `map[Continent]` function:

```{r}
mapAsia(1900)
```

Six options are available:

-   `mapNorthAmerica()`

-   `mapSouthAmerica()`

-   `mapEurope()`

-   `mapAfrica()`

-   `mapAsia()`

-   `mapOceania()`

## Mapping Regions 

To plot a region of the world, users can use the `mapRegion()` function to map a region on a given year with `mapRegion([year],["region"])`:

```{r}
mapRegion(1825, "Eastern Europe")
```

## Mapping Countries 

If a user wants to visualize a specific country at a specified time, they can input the year and country name to the function `mapCountry()`to give a map of that country's borders. The user should input `mapCountry([year], ["country name"])`:

```{r}
mapCountry(1900, "United States")
```

## Custom Mapping

If a user wants to only visualize a certain area of the world, they can visualize a custom area using coordinate pairs. The function `mapCustom()` will map a given are on a given year by `mapCustom([year], [pair of latitudes], [pair of longitudes])`:

```{r}
mapCustom(1900, c(20, 65), c(15, 45))
```
